Karbowski model in 2-D

### 2020-05-20 paper/supplementary/supp.tex
Updates to supplementary, plus pdf for convenience

Change the flux current to:
%
\begin{equation} \label{eq:J_NM_with_comp6}
\mb{J}_i(\mb{x},t) = D \nabla a_i(\mb{x},t)
+ \bar{a}_i(\mb{x}, t)  \sum_{p \ne i}  \zeta_{i,p} \nabla {a}_p(\mb{x}, t) -
a_i(\mb{x}, t) \, \mb{g}(\mb{x})
\end{equation}
%
where $\bar{a}_i$ is a sigmoid of height $h$, offset $o$ and
sharpness, $s$:
\begin{equation}
\bar{a}_i = \frac{h}{1 + e^{(o - s \, a_i)}}
\end{equation}
%
used for the same reason as in section \ref{sec:comp2}.

@@

The mechanism works quite nicely, and has the advantage of using only
graded guidance molecule expression.
See \code{configs/whiskers/5N\_boundedorder.json}
%
% BIBLIOGRAPHY
%
\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
% The bibliography NoTremor.bib is the one exported from Zotero. It
% may be necessary to run my UTF-8 cleanup script, bbl_utf8_to_latex.sh
%%\bibliography{NoTremor}
%
% It produces this:
\begin{thebibliography}{1}

>>>>

Change the flux current to:
%
\begin{equation} \label{eq:J_NM_with_comp6}
\mb{J}_i(\mb{x},t) = D \nabla a_i(\mb{x},t)
+ \bar{a}_i(\mb{x}, t)  \sum_{p \ne i}  \zeta_{i,p} \nabla {a}_p(\mb{x}, t) -
a_i(\mb{x}, t) \, \mb{g}(\mb{x})
\end{equation}
%
where $\bar{a}_i$ is a sigmoid of height $h$, offset $o$ and
sharpness, $s$:
\begin{equation}\label{eq:abar}
\bar{a}_i = \frac{h}{1 + e^{(o - s \, a_i)}}
\end{equation}
%
used for the same reason as in section \ref{sec:comp2}.

@@

The mechanism works quite nicely, and has the advantage of using only
graded guidance molecule expression.
See \code{configs/whiskers/5N\_boundedorder.json}

\section {Post eLife Review work}

One of the reviewers, Bard Ermentrout, suggested an alternative formulation of
the branching competition, to avoid the undesirable need to divisively
normalize the branching density at each simulation step.

The suggestion was to let the $\chi$ term from Eq.~3 of the preprint be given
by:

\begin{equation}\label{eq:chibard}
\chi_i = \frac{a_i}{N-1} \nabla\hat{a}_i,
\end{equation}

where $\hat{a}_i$, the sum of branching over all other TC types, is given by
Eq.~\ref{eq:ahat}. Implementing Eq.~\ref{eq:chibard} gives:

\begin{equation} \label{eq:dabard}
\frac{\partial a_i}{\partial t} =
\nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right)
+ \frac{a_i}{N-1} \nabla\hat{a}_i
- \frac{\partial c_i}{\partial t}.
\end{equation}

There's a problem here. The problem is that the gradient of $\hat{a}_i$ is
a \emph{vector} quantity whereas $\dot{a}_i$ is scalar. So in fact, Bard's
suggestion doesn't make good sense as written.

Compare this with Eq.~\ref{eq:J_NM_with_comp} from Section \ref{sec:comp2},
which was one of the competition types I tried fairly early on. In fact, it
was my second idea for competition. It's similar, but not identical. Written
out in the same style as Eq.~\ref{eq:dabard} it is:

\begin{equation} \label{eq:da_comp2_elife}
\frac{\partial a_i}{\partial t}
= \nabla\vcdot  \left(D \nabla a_i
- a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})
+ \frac{\bar{a}_i F}{N-1} \nabla \hat{a}_i \right)
- \frac{\partial c_i}{\partial t}.
\end{equation}

This modifies the axon branching with a similar term to Eq.~\ref{eq:chibard},
depending on the gradient of $\hat{a}_i = \sum_{j\ne i}{a_j}$. However, here,
the term is included in the \emph{flux of axonal branching}
(i.e.~\emph{inside} the brackets) and so its divergence is taken and this
contributes a scalar quantity to the change of $a_i$. Two other points to note
about Eq.~\ref{eq:da_comp2_elife}: I included a scalar parameter $F$ to modify
the relative contribution of this term; and $\bar{a}_i$ is the result of
passing $a_i$ through a sigmoidal transfer function (see Eq.~\ref{eq:abar})
which I found necessary to prevent the term from becoming numerically
unstable.

I passed Eq.~\ref{eq:da_comp2_elife} over for the preprint, because the
competition it produced seemed weak, and I was relying on the development of
contours and `well localized regions' to indicate success.

After re-examining the effect of \code{rd\_james\_comp2}, which expresses
Eq.~\ref{eq:da_comp2_elife}, I found that it does provide competition enough
to generate a barrel-field-like ordering, when the argmaxes of the $N$ $c_i$
values are plotted, as in the preprint.

\begin{equation}\label{eq:chibard_mag}
\chi_i = \frac{a_i}{N-1} \| \nabla\hat{a}_i\|.
\end{equation}

%
% BIBLIOGRAPHY
%
\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
% The bibliography NoTremor.bib is the one exported from Zotero. It
% may be necessary to run my UTF-8 cleanup script, bbl_utf8_to_latex.sh
%%\bibliography{NoTremor}
%
% It produces this:
\begin{thebibliography}{1}
